---
title: "A prediction market for malaria elimination: harnessing the wisdom of crowds to inform health financing and policy"
date: ''
output: 
  pdf_document:
    includes:
      in_header: preamble.sty
fig_width: 4
fig_height: 2.6
bibliography: bibliography.bib
---


```{r, echo = FALSE, warning = FALSE, message = FALSE, comment = NA, error= FALSE, cache = FALSE}
# Packages
library(tidyverse)
library(knitr)
library(Hmisc)
library(malariaprediction)
library(knitr)
library(googleVis)
library(RColorBrewer)

## Global options
options(max.print="75")
opts_chunk$set(echo=FALSE,
	             cache=TRUE,
               prompt=FALSE,
               tidy=TRUE,
               comment=NA,
               message=FALSE,
               warning=FALSE)
opts_knit$set(width=75)
```


\begin{center}
\begin{large}

```{r, results = 'asis', eval = TRUE}
# malariaprediction::make_authors()
```

\end{large}
\end{center}

\vspace{5mm}

\begin{center}
\textbf{Abstract}  
\end{center}

\vspace{5mm}
\begin{center}
\begin{changemargin}{3cm}{3cm} 

Here goes some abstract text. Bla bla bla bla bla bla bla bla bla bla bla bla bla bla bla bla bla bla bla bla bla bla bla bla bla bla bla bla bla bla bla bla bla bla bla bla bla bla bla bla bla bla bla bla bla bla bla bla bla bla bla bla bla bla bla bla bla bla bla bla bla bla bla .

\end{changemargin}
\end{center}




# Introduction

- Need for accurate information regarding malaria elimination's feasibility.  
- Current sources of information are biased.  
- Prediction market address those biases.


# Methods

We created

All data processing and analysis were carried out in R [@R]. All code is freely available online [@brewgit].

# Results

Some text goes here


# Discussion

Some text goes here



```{r, eval=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'knitr', 'rmarkdown'
), 'packages.bib')
```


# References



